\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2019-11-25 sections/coverpage.tex
Update coverpage for final draft

  \vspace*{\fill}
  { \huge \bfseries Correlating Microbial Abundances for the Microbial Interaction Network Database}\\[0.4cm] % Title of your document

@@

  % \vspace{1.5 cm}
  % Dileep Kishore\textsuperscript{1},
  % Gabriel Birzu\textsuperscript{2},
  % Zhenjun Hu\textsuperscript{1},
  % Charles DeLisi\textsuperscript{1,3},
  % Kirill Korolev\textsuperscript{1,2},
  % Daniel Segr\`{e}\textsuperscript{1,3,4}\\
  % \vspace{1cm}
  % \textsuperscript{1}Bioinformatics Program, Boston University, Boston, Massachusetts, USA\\
  % \textsuperscript{2}Department of Physics, Boston University, Boston, Massachusetts, USA\\
  % \textsuperscript{3}Department of Biomedical Engineering, Boston University, Boston, Massachusetts, USA\\
  % \textsuperscript{4}Department of Biology, Boston University, Boston, Massachusetts, USA\\

>>>>

  \vspace*{\fill}
  {\huge Inferring microbial co-occurrence networks from 16S data: A systematic evaluation}\\[0.4cm]
  % {\huge  2. Investigating the best practices for inference of microbial co-occurrence networks from 16S data}\\[0.4cm] % Title of your document
  % {\huge  3. Attempting to find the best practice pipeline for inferring co-occurrence networks from 16S data}\\[0.4cm] % Title of your document
  % {\huge  4. Deciphering the complexities in co-occurrence network inference from 16S data}\\[0.4cm] % Title of your document

@@

  \vspace{1.5 cm}
  Dileep Kishore\textsuperscript{1},
  Gabriel Birzu\textsuperscript{2},
  Zhenjun Hu\textsuperscript{1},
  Charles DeLisi\textsuperscript{1,3},
  Kirill Korolev\textsuperscript{1,2},\\
  Daniel Segr\`{e}\textsuperscript{1,3,4}\\
  \vspace{1cm}
  \textsuperscript{1}Bioinformatics Program, Boston University, Boston, Massachusetts, USA\\
  \textsuperscript{2}Department of Physics, Boston University, Boston, Massachusetts, USA\\
  \textsuperscript{3}Department of Biomedical Engineering, Boston University, Boston, Massachusetts, USA\\
  \textsuperscript{4}Department of Biology, Boston University, Boston, Massachusetts, USA\\
